A pipeline to analyse time-course gene expression data

### 2020-08-11 scripts/manuscript.Rmd
add check on version number of moanin

```{r eval=FALSE}
BiocManager::install(c("NMF","ggfortify","topGO","biomaRt","KEGGprofile","BiocWorkflowTools"))
```

@@

- **Elbow method**. First introduced in 1953 by Thorndike [@thorndike:who],
  the elbow methods looks at the total with cluster sum of squares 
  as a function of the number of clusters (WCSS). When adding clusters
  doesn't decrease the WCSS by a sufficient
  amount, one can consider stopping. This method thus provides visual aid to
  the user to choose the number of clusters, but often the "elbow" is hard to
  see on real data, where the number of clusters is not clearly defined.
- **Silhouette method**. Similarly to the Elbow method, the Silhouette method
  refers to a method of validation of consistency within clusters, and
  provides visual aid to choose the number of clusters.
- **Stability methods** Stability methods are more computationally intensive
  than any other method, as they rely on assessing the stability of the
  clustering for every $k$ to a small randomization of the data. The user is
  then invited to choose the number of cluster based on a number of similarity
  measures.

@@

```{r,echo=FALSE}
kable(head(stability_5))
```

@@

# Select the columns to print and give nicer column names
pathways = subset(
    pathways,
    select=c(
	"Pathway_Name", "Percentage",
	"pvalueAdj"))
colnames(pathways) = c("Pathway", "Percentage", "Adj. p-value")
pathways["Percentage"] = pathways["Percentage"] * 100
kable(pathways[1:min(10,nrow(pathways)), ], format="latex", escape=F, digits=4, booktabs=TRUE)
```

>>>>

```{r eval=FALSE}
BiocManager::install(
    c("NMF", "ggfortify", "topGO", "biomaRt",
      "KEGGprofile", "BiocWorkflowTools"))
```

@@

- **Elbow method**. First introduced in 1953 by Thorndike [@thorndike:who],
  the elbow methods looks at the total within cluster sum of squares 
  as a function of the number of clusters (WCSS). When adding clusters
  doesn't decrease the WCSS by a sufficient
  amount, one can consider stopping. This method thus provides visual aid to
  the user to choose the number of clusters, but often the "elbow" is hard to
  see on real data, where the number of clusters is not clearly defined.
- **Silhouette method**. Similarly to the Elbow method, the Silhouette method
  refers to a method of validation of consistency within clusters, and
  provides visual aid to choose the number of clusters.
- **Stability methods** Stability methods are more computationally intensive
  than any other method, as they rely on assessing the stability of the
  clustering for every $k$ to a small randomization of the data. The user is
  then invited to choose the number of cluster based on a number of similarity
  measures.

@@

```{r,echo=FALSE}
kable(head(stability_5)) %>%
  kable_styling(font_size = 7)
```

@@

# Select the columns to print and give nicer column names
pathways = subset(
    pathways,
    select=c(
	"Pathway_Name", "Percentage",
	"pvalueAdj"))
colnames(pathways) = c("Pathway", "Percentage", "Adj. p-value")
pathways["Percentage"] = pathways["Percentage"] * 100
kable(pathways[1:min(10,nrow(pathways)), ],
      format="latex",
      escape=F,
      digits=4,
      booktabs=TRUE) %>%
  kable_styling(font_size = 7)
```
